A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility.

### 2020-02-05 paper.Rmd
Update paper.Rmd
Typo
mention OSF - closes #112

A Digital Object Identifier (DOI), is a unique identifier for a digital object such as a paper, poster, or software, and is a prerequisite for citation. For example, if the data are deposited in repositories like Dryad or Zenodo, the best practice would be to copy the citation created by these repositories. Under the hood, the DOI is "minted" by DataCite, who provide DOIs for research outputs and data. This means that when citing data, it only makes sense to cite datasets that have been deposited into a DataCite compliant repository. If a DOI is unavailable, a citation will be meaningless, as it cannot be tracked by any means. A file named `citation` should be placed in the directory, at the same level as the `README`. It should contain a DOI, and could be in `.bibtex` format.

@@

If the dataset you are shipping has a research application, the most relevant home would be the research data repositories **zenodo** or **dryad**. Zenodo, Launched in 2013 in a joint collaboration between openAIRE and CERN, provides a free, archival location for any researcher to deposit their datasets. The only limits to file sizes are 50gb for individual files, which is generous enough to accommodate a large number of use cases. Zenodo is able to accommodate larger file sizes upon request. The Dryad Digital Repository (@dryad) will take data from any field of research, and perform human quality control and assistance  of the data, with the ability to link data with a journal publication, in exchange for a data publishing fee.

>>>>

A Digital Object Identifier (DOI), is a unique identifier for a digital object such as a paper, poster, or software, and is a prerequisite for citation. For example, if the data are deposited in repositories like Dryad, Zenodo, or the Open Science Framework, the best practice would be to copy the citation created by these repositories. Under the hood, the DOI is "minted" by DataCite, who provide DOIs for research outputs and data. This means that when citing data, it only makes sense to cite datasets that have been deposited into a DataCite compliant repository. If a DOI is unavailable, a citation will be meaningless, as it cannot be tracked by any means. A file named `citation` should be placed in the directory, at the same level as the `README`. It should contain a DOI, and could be in `.bibtex` format.

@@

If the dataset you are shipping has a research application, the most relevant home would be the research data repositories **zenodo**, **dryad**, or **Open Science Framework**. Zenodo, Launched in 2013 in a joint collaboration between openAIRE and CERN, provides a free, archival location for any researcher to deposit their datasets. The only limits to file sizes are 50gb for individual files, which is generous enough to accommodate a large number of use cases. Zenodo is able to accommodate larger file sizes upon request. The Dryad Digital Repository (@dryad) will take data from any field of research, and perform human quality control and assistance  of the data, with the ability to link data with a journal publication, in exchange for a data publishing fee. The OSF is a tool that captures the research process online. This ranges from conceiving research ideas, study design, writing papers, to storing research data. The entire history of the project is recorded, so it promotes centralized, and transparent workflows. Although not specifically designed for data, like Dryad or Zenodo, OSF does provide a DOI minting service, and a more wholistic approach, which might be appealing to users [@OSF].
